From Nested Virtualization Architecture \\To 2D Security Management for Distributed Clouds

### 2014-03-21 paper/draft.tex
Updated requirements.

@@

We identified five key design principles that a IaaS architecture should implement to meet the previous challenges. In what follows, those principles will serve as reading template to analyze different architectures.
\begin{itemize}[]
\item \textbf{DP1 User-Data Privacy} A curious or malicious administrator (or another platform user) should not be authorized to inspect and analyze user data and VM instances without explicit user consent relying on mutually trusted services. A trade-off should be found to allow providers to detect and react to potential threats, but also to prevent unlimited platform and user data access in such inappropriate operator behaviors. Thus, a platform administrator should not manage the infrastructure directly using the highest level of privilege. Instead, his actions on user data objects should be validated by a mutually-trusted kernel run in the most privileged mode. This kernel should also enforce memory page encryption to prevent snooping when pages are swapped out.
\item \textbf{DP2 Fail-Safe Modular Architecture} In order to recover soft failures, the archtecure is supposed to be fail-safe, being able of automatically migrate instances or user-data in presence of a menace, but also reactivating the correct functioning in presence of a software failure. In order to satisfy this property, the amount of safety-critical components has to be as lowest as possible and the overall design has to be kept as modular as possible.
\item \textbf{DP3 Small TCB} The amount of lines of code executed at the highest level of privilege is normally proportional to the number of potential failures and bugs in the platform. According to this, an architecture presenting a tiny TCB will improve its safety and integrity properties by design.
\item \textbf{DP4 Inter-Platform Support} The cloud architecture has to be designed in order to support directly different platforms and service providers. The same user virtual instances have to be executed (and potentially migrated) unmodified over different platforms.
\item \textbf{DP5 Compatibility with Legacy} Avoid disruption of existing 3rd part applications compatibility could represent a major principle to consider. Platform interfaces has to be kept as close as possible to the existing one, preventing application rewrite.
\end{itemize}
Moreover, beside this functional design principles specifying which features have to be achieved by the platform, another set of non-design principles could be identified. Those principles does not concern directly features or aspects of the architecture of the platform, but the effective feasibility of the architecture. 
\begin{itemize}[]
\item \textbf{NDP1 Minimize code addition} a major issue could be represented by the amount of code lines that have to be added and maintained to an existing architecture to meet the functional requirement. Even it does not represent strictly a technical limitation to a certain proposal, it could become a ``show-stopper'' factor for its utilization.
\end{itemize}
In our analysis, it will be kept in consideration not only the overall suitability of the architecture, but also a quantification of the effort needed to develop and deploy it. In table \ref{int:des} it is possible to observe a resume of previous cited principles.

\begin{table}
\label{int:des}
\begin{tabular}{llll}
\toprule
Id & Functional design Principle & Class &\\
\midrule
DP1 & User-Data privacy & Vertical & \\
DP2 & Fail-Safe modular architecture & Vertical & \\ 
DP3 & Small TCB & Vertical & \\
DP4 & Inter-platform support & Horizontal & \\
DP5 & Backwards 3rd part compatibility & Horizontal \\
NDP1 & Minimize code addition & & \\
\bottomrule
\end{tabular}
\end{table}

This paper is organized as following. In Section~\ref{sec:rw} we analyze the nested virtualization ecosystem and position existing solutions regarding our design principles. In Section~\ref{sec:classic}, we details limitations of classical nested virtualization approach and in Section~\ref{sec:mh} we present the microvisor approach. In Section~\ref{sec:archcomp} we compare cloud architectures propositions, combining nested virtualization and microvisors, leveraging the design principles grid introduced before.
%Furthermore, in Section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles.
In Section~\ref{sec:conclu}, we conclude the paper with future works and our vision of the SuperCloud.
% in section in section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles. In section 8, we conclude the paper with future works in section 8.

>>>>

This paper is organized as follows. In Section~\ref{sec:rw} we analyze the nested virtualization ecosystem and position existing solutions regarding our design principles. In Section~\ref{sec:classic}, we details limitations of classical nested virtualization approach and in Section~\ref{sec:mh} we present the microvisor approach. In Section~\ref{sec:archcomp} we compare cloud architectures propositions, combining nested virtualization and microvisors, leveraging the design principles grid introduced before.
%Furthermore, in Section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles.
In Section~\ref{sec:conclu}, we conclude the paper with future works and our vision of the SuperCloud.
% in section in section 6 we define a security architecture for multi-cloud scenario, with an analysis of necessary software components to satisfy vertical design principles. In section 8, we conclude the paper with future works in section 8.

\section{Challenges and Design Principles}

@@

We identified five key design principles (DP) that a IaaS architecture should implement to meet the previous challenges. In what follows, those principles will serve as reading template to analyze different architectures.
\begin{itemize}[]
\item \textbf{DP1 User Data Privacy} A curious or malicious administrator (or another platform user) should not be authorized to inspect and analyze user data and VM instances without explicit user consent relying on mutually trusted services. A trade-off should be found to allow providers to detect and react to potential threats, but also to prevent unlimited platform and user data access in such inappropriate operator behaviors. Thus, a platform administrator should not manage the infrastructure directly using the highest level of privilege. Instead, his actions on user data objects should be validated by a mutually-trusted kernel run in the most privileged mode. This kernel should also enforce memory page encryption to prevent snooping when pages are swapped out.
\item \textbf{DP2 Fail-Safe Modular Architecture} The architecture should be fail-safe: for instance, to enable automatically migration of instances or user-data in presence of a threat and to recover from software failures. To reach this goal, the amount of safety-critical components should be as low as possible to mimize the attack surface. Similarly, the overall design should be as modular as possible to enable platform reconfiguration.
\item \textbf{DP3 Small TCB} The number of potential failures and bugs in the platform is directly linked with the code size executed at the highest level of privilege. Thus, an architecture with a tiny TCB (Trusted Computing Base) will improve safety and integrity by design.
\item \textbf{DP4 Inter-Platform Support} The cloud architecture should allow supporting directly different platforms and service providers. The same user virtual instances should be allowed to be run (and potentially migrated) unmodified over different IaaS platforms.
\item \textbf{DP5 Compatibility with Legacy} Evolution in the IaaS architecture should avoiding disrupting existing third party applications. Thus, platform interfaces should be kept as close as possible to existing ones, to prevent code rewriting notably for applications.
\end{itemize}
In addition to the above functional design principles that specify which features have to be achieved by the platform architecture, another set of non-design principles (NDP) should be considered regarding effective feasibility of implementing the architecture. We just give an example in terms of platform usability:
\begin{itemize}[]
\item \textbf{NDP1 Minimal Additional Code} A major issue could be represented by the amount of code to be added and maintained to an existing architecture to meet functional requirements. Despite not being a strictly a technical limitation of the architecture, it could become a show-stopper to its practical use.
\end{itemize}
In our analysis, we will consider not only the overall suitability of the architecture, but also the amount of effort needed to develop and deploy it. Table \ref{int:des} summarizes the previous principles and which class of requirements they address.

\begin{table}
\caption{Design Principles for a Distributed IaaS Platform.\label{int:des}}
\begin{tabular}{lll}
\toprule
\textbf{Id} & \textbf{Design Principle} & \textbf{Class of Requirement} \\
\midrule
DP1 & User Data Privacy & Vertical \\
DP2 & Fail-Safe Modular Architecture & Vertical \\ 
DP3 & Small TCB & Vertical \\
DP4 & Inter-Platform Support & Horizontal \\
DP5 & Compatibility with Legacy & Horizontal \\
NDP1 & Minimal Additional Code & -- \\
\bottomrule
\end{tabular}
\end{table}
